\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{JAIHYUN PARK\\}
\normalsize 535 W Michigan St. IT 581, Indianapolis, IN 46202 \\ 
\normalsize jaipark@iu.edu $\mid$ ORCID:0000-0001-6217-7192 $\mid$ https://github.com/park-jay \\
\hrulefill
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROFESSIONAL EXPERIENCE}} \\
\noindent \textbf{Department of Library and Information Science, Luddy School of Informatics, Computing, and Engineering} \\
\noindent \textbf{Indiana University Indianapolis} \hfill Indianapolis, IN \\
\noindent \textit{Assistant Professor} \hfill August 2025 - Present \\

\noindent \textbf{Wee Kim Wee School of Communication and Information, Nanyang Technological University} \hfill Singapore \\
\noindent \textit{Assistant Professor} \hfill August 2024 - July 2025 \\

% \vspace{0.5cm}

\noindent \textbf{\underline{EDUCATION}} \\
\noindent \textbf{School of Information Sciences, University of Illinois at Urbana-Champaign} \hfill Champaign, IL \\
\noindent{\textit{Ph.D. in Information Sciences}} \hfill 2019-2024\\
\noindent{Advisor: Ryan Cordell}\\
\noindent{Dissertation: A Computational Approach Toward Understanding the Political Language of Ideologically Opposing Groups – From Historical Newspapers to Social Media} \hfill \href{https://hdl.handle.net/2142/125699}{Dissertation} \\

\noindent \textbf{School of Information Studies, Syracuse University} \hfill Syracuse, NY \\
\noindent{\textit{M.S. in Library and Information Science}} \hfill 2017-2019 \\
\noindent{\textit{Certificate of Advanced Study in Data Science}} \hfill \\
\noindent{Advisor: Jian Qin} \\

\noindent \textbf{Yonsei University} \hfill Seoul, South Korea \\
\noindent{\textit{B.A. in Library and Information Science}} \hfill 2010-2017 \\
\noindent{\textit{B.A. in Political Science and International Relations}} \hfill \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{RESEARCH INTEREST}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Digital Humanities / Computational Social Science}
\begin{itemize}
    \item {Natural Language Processing (Comparative / Quantitative Discourse Analysis)}
    \item {Network Analysis}
\end{itemize}
\item {Responsible Data Science}
    \begin{itemize}
        \item {Data Curation (Data Reuse and Sharing)}
    \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5cm}
\noindent \textbf{\underline{AWARDED PAPERS}} \\
\noindent \textbf{Park, J.} (2016). The Federated Library for North and South Korea to Preserve Collective Knowledge. \textit{The 2016 Unification Thesis Collection: The 35th (Under) Graduate Student Unification Thesis Award}, 35, pp. 123-170 (in Korean). \hfill \href{https://uniedu.go.kr/uniedu/home/pds/pdsatcl/view.do?id=19773&mid=SM00000532&limit=20&sc=T&eqOdrby=false&eqViewYn=true&odr=news}{Paper}\\ 

\noindent \textbf{Park, J.} (2014). Advancing Collection Quality to Modernize Libraries - Through Librarian Collaborative Book Review. \textit{The Awarded Thesis Collection: The 6th (Under) Graduate Student Library Modernization Thesis Award}, 6, pp. 39-64 (in Korean). \hfill \href{https://oak.go.kr/nl-ir/handle/2020.oak/304}{Paper}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{JOURNAL PUBLICATIONS}} \\
\noindent Kim, S., Yoon, A. \& \textbf{Park, J.} (2025). Research Trends in STEM Education: A Review of Publicly Funded Projects from the Institute of Museum and Library Services. \textit{Library and Information Science Research}. \hfill \href{https://www.sciencedirect.com/science/article/abs/pii/S0740818825000295}{Paper} \\

\noindent \textbf{Park, J.}, Yang, JH., Tolbert, A. \& Bunsold, K. (Online First). You change the way you talk: Examining the network, hate speech, and discourse of cross-platform users on Twitter and Parler during the 2020 U.S. Presidential Election. \textit{Journal of Information Science}. \hfill \href{https://journals.sagepub.com/doi/abs/10.1177/01655515241238405}{Paper} \href{https://github.com/park-jay/cross-platform}{Code} \\ 

\noindent \textbf{Park, J.} \& Cordell, R. (Online First). The ripple effect of dataset reuse: Contextualising the data lifecycle for machine learning data sets and social impact. \textit{Journal of Information Science}. \hfill \href{https://journals.sagepub.com/doi/abs/10.1177/01655515231212977}{Paper} \\

\noindent Dalgali, A., Xiao, L. \& \textbf{Park, J.} (2023). Reasoning in Social Media: Insights from Reddit "Change My View" Submissions. \textit{Online Information Review}, 45(7), pp. 1208-1226. \hfill \href{https://www.emerald.com/insight/content/doi/10.1108/OIR-08-2020-0330/full/html}{Paper} \\

\noindent \textbf{\underline{CONFERENCE \& WORKSHOP PAPERS}} \\ 
\noindent \textbf{Park, J.} \& Cordell, R. (2025). A data-driven investigation of euphemistic language: Comparing the usage of ``slave'' and ``servant'' in 19th century US newspapers. \textit{NLP4DH 2025}. \hfill \href{https://aclanthology.org/anthology-files/anthology-files/pdf/nlp4dh/2025.nlp4dh-1.31.pdf}{Paper} \href{https://github.com/park-jay/slavery-discourse}{Code} \\

\noindent Griebel, S., Cohen, B., Lucian, L., \textbf{Park, J.}, Liu, J., Perkins, J. \& Underwood, T. (2024). Locating the Leading Edge of Cultural Change. \textit{The Fifth Conference on Computational Humanities Research}. \hfill \href{https://arxiv.org/pdf/2411.15068}{Paper} \href{https://github.com/IllinoisLiteraryLab/novelty}{Code} \\

\noindent \textbf{Park, J.} \& Cordell, R. (2023). A Quantitative Discourse Analysis of Asian Workers in the US Historical Newspapers. \textit{The Joint 3rd International Conference on NLP4DH \& IWCLUL} pp. 7-15. \hfill \href{https://aclanthology.org/2023.nlp4dh-1.2/}{Paper} \href{https://github.com/park-jay/coolie}{Code}\\

\noindent Liu, B., Zhou, Z., Zhu, D. \& \textbf{Park, J.} (2023). Understanding Gender Stereotypes in Video Game Character Designs. A Case Study of Honor of Kings. \textit{The Joint 3rd International Conference on NLP4DH \& IWCLUL} pp.125-131. \hfill \href{https://arxiv.org/pdf/2311.14226}{Paper} \\

\noindent \textbf{Park, J.} \& Jeoung, S. (2022). Raison d'être of the benchmark dataset: A Survey of Current Practices of Benchmark Dataset Sharing Platforms. \textit{NLP Power! The First Workshop on Efficient Benchmarking in NLP at Association for Computational Linguistics} pp.1-10. \hfill \href{https://aclanthology.org/2022.nlppower-1.1/}{Paper} \\

\noindent Dobreski, B., \textbf{Park, J.}, Leathers, A. \& Qin, J. (2019). Remodeling Archival Metadata Descriptions for Linked Archives. \textit{The International Conference on Dublin Core and Metadata Applications} pp.1-11. \hfill \href{https://dcpapers.dublincore.org/article/952141553}{Paper} \\ 

\noindent Allen, R. B. \& \textbf{Park, J.} (2018). Coordinating and Integrating Faceted Classification with Rich Semantic Modeling. \textit{The Workshop on Ontology and Rich Semantics: Frameworks and Applications} \hfill \href{https://arxiv.org/abs/1809.09548}{Paper} \\

\noindent \textbf{\underline{CONFERENCE POSTERS \& EXTENDED ABSTRACT}} \\
\noindent \textbf{Park, J.}, Yoon, A. (2025). Characteristics of Dataset and Model Reuse Patterns on the Hugging Face Platform. \textit{The 88th Annual Meeting of the Association for Information Science and Technology (ASIS\&T).} \hfill \\ \href{https://doi.org/10.1002/pra2.1490}{Paper} \href{https://github.com/park-jay/huggingface-models}{Code} \\

% \noindent \textbf{Park, J.}, Kim, Y.E. \& Chung, W.Y. (Submitted). Evaluating the Impact of Large Language Models on Environmental Decision-Making: A Comparative Study of Western and Chinese LLMs. \textit{The 2025 International Association for Media and Communication Research (IAMCR).} \\  

\noindent \textbf{Park, J.}, Seo, J. \& Lee, J. (2023). Exploring an Online Community of Blind Programmers by Using Topic Modeling and Network Analysis. \textit{The 86th Annual Meeting of the Association for Information Science and Technology (ASIS\&T)} \hfill \href{https://doi.org/10.1002/pra2.956}{Paper} \\

\noindent \textbf{Park, J.}, Yang, JH., Bunsold, K. \& Tolbert, A. (2022). Cross-platform Analysis of Twitter and Parler during the 2020 U.S. Presidential Election. \textit{International Communication Association Conference (ICA).} \hfill \href{https://www.ideals.illinois.edu/items/121292}{Paper} \\ 

\noindent Rezapour, R., \textbf{Park, J.} \& Diesner, J. (2020). Detecting Characteristics of Cross-cutting Language Networks on Social Media. \textit{The International Sunbelt Social Network Conference (INSNA)}. \\

\noindent Mishra, R., \textbf{Park, J.} \& Diesner, J. (2020). Leveraging Topic Modeling to Enhance the Interpretability of Stance Detection. \textit{The 6th Annual International Conference on Computational Social Science (IC2S2)}. \\

\noindent Rezapour, R., \textbf{Park, J.} \& Diesner, J. (2020). Detecting Characteristics of Cross-cutting Language Networks on Social Media. \textit{The 6th Annual International Conference on Computational Social Science (IC2S2)}. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{COURSES}} 

\noindent \textbf{Luddy School of Informatics, Computing, and Engineering, Indiana University Indianapolis} \hfill Indianapolis, IN \\
\noindent{Python for Information Professionals (LIS-S 604) \textit{Instructor}} \hfill Spring 2026 \\
\noindent{Python for Information Professionals (LIS-S 604) \textit{Co-Instructor with Dr. Austin Stroud}} \hfill Fall 2025 \\

\noindent \textbf{Wee Kim Wee School of Communication and Information, Nanyang Technological University} \hfill Singapore \\
\noindent{Social Media Analytics (IS 6750) \textit{Instructor}} \hfill Fall 2024, Spring 2025 \\
% \noindent{Digital Libraries (IS 6730) \textit{Instructor}} \hfill Spring 2025 \\ 

\noindent \textbf{School of Information Sciences, University of Illinois at Urbana-Champaign} \hfill Champaign, IL \\
\noindent{Social Media Analysis (IS 324) \textit{Instructor}} \hfill Spring 2024 \\
\noindent{Reference and Information Services (IS 501) \textit{Teaching Assistant}} \hfill Summer 2021, 2023 \\
\noindent{Ethics and Policy for Data Science (IS 467) \textit{Teaching Assistant}} \hfill Fall 2022 \\
\noindent{Information Modeling (IS 515) \textit{Teaching Assistant}} \hfill Fall 2021 \\
\noindent{Information Organization and Access (IS 505) \textit{Teaching Assistant}} \hfill Spring 2021 \\
\noindent{Foundations of Information Processing (IS 430) \textit{Teaching Assistant}} \hfill Fall 2020 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{HONORS \& AWARDS}} \\
\noindent Social Media Research Competition, SIG-SM ASIS\&T 2025 (Honorable Mention) \hfill 2025 \\
\noindent Eugene Garfield Doctoral Dissertation Fellowship, Beta Phi Mu Society (USD 3,000) \hfill 2024 \\
\noindent Doctoral Colloquium Award, ASIS\&T (USD 425: The conference registration fee) \hfill 2023 \\
\noindent Master's Award, Syracuse University (USD 500) \hfill 2019 \\
\noindent D. Whitney Coe Scholarship, Syracuse University (USD 14,030) \hfill 2018-2019 \\
\noindent D. Whitney Coe Scholarship, Syracuse University (USD 4,677) \hfill Summer 2018 \\
\noindent D. Whitney Coe Scholarship, Syracuse University (USD 13,500) \hfill 2017-2018 \\
\noindent The 35th Korea Unification Thesis Award, Ministry of Unification (3rd Place, KRW 2,000,000) \hfill 2016 \\
\noindent The 6th Library Modernization Thesis Award, National Library of Korea (2nd Place, KRW 1,000,000) \hfill 2014 \\
\noindent The Excellent Student Scholarship, Yonsei University (KRW 2,289,000)
\hfill 2014 \\
\noindent The Excellent Student Scholarship, Yonsei University (KRW 1,181,300) \hfill 2013 \\

% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{GRANT PROJECTS}} 

\noindent Examining Linguistic Characteristics of AI-written News Articles \hfill 2024 \\
\null \hfill Start-up Grant: Nanyang Technological University \\
\textit{Principal Investigator} 
\null \hfill SGD 35,000 \\

\noindent A Computational Text Analysis on Stereotying in Online Communities \hfill 2024 \\
\null \hfill Academic Research Fund (AcRF) Tier 1 Seed Funding Grant: Ministry of Education, Singapore \\
\textit{Principal Investigator} 
\null \hfill SGD 50,000 \\

\noindent The Virality of Racial Terror in US Newspapers, 1863-1921 \hfill 2023 \\
\null \hfill Mellon Foundation Reference: \href{https://www.mellon.org/grant-details/the-virality-of-racial-terror-in-us-newspapers-1863-1921-20452145}{2204-12741}  \\
\textit{Research Assistant} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{PRESS}} \\
\noindent Kallenback, J. (2020). Library students greatly impact CU. \textit{The Daily Illini}. \hfill \href{https://dailyillini.com/life_and_culture-stories/2020/11/11/library-students-greatly-impact-cu/}{Article} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{STUDENT MENTORSHIP}} \\

\noindent \textbf{Indiana University Indianapolis} \hfill Indianapolis, IN \\
\noindent \textit{Ph.D. Advisor} \\
\noindent Hasaranga Dilshan Jayathilake (Ph.D. in Library and Information Science) \hfill Fall 2025 - Present \\

\noindent \textbf{Wee Kim Wee School of Communication and Information, Nanyang Technological University} \hfill Singapore \\
\noindent \textit{Dissertation Committee} \\ 
\noindent Shilan Huang (Ph.D. in Communication and Information) \hfill Fall 2024 - Spring 2024 \\

\noindent \textit{Qualifying Examination Committee} \\
\noindent Qiu Haoran (Ph.D. in Communication and Information) \hfill Fall 2024 \\

\noindent \textbf{School of Information Sciences, University of Illinois at Urbana-Champaign} \hfill Champaign, IL \\
\noindent Jae Young Lee (Undergraduate in Information Sciences) \hfill Fall 2023 - Spring 2024 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{SERVICE}} \\
\noindent \textbf{Wee Kim Wee School of Communication and Information, Nanyang Technological University} \hfill Singapore \\
\noindent \textit{MS in Information Systems Admission Committee} \hfill 2025 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{MEMBERSHIP}} \\ 
\noindent ACL (Association for Computational Linguistics) \\
\noindent ASIS\&T (Association for Information Science and Technology) \\
\textit{Reviewer} \hfill \href{https://www.asist.org/meetings-events/am/am23/2023-annual-meeting-reviewers/}{2023}, \href{https://www.asist.org/meetings-events/am/am24/2024-annual-meeting-reviewers/}{2024}\\
\noindent NLP4DH (Natural Language Processing for Digital Humanities) \\
\textit{Programs Committees} \hfill \href{https://www.nlp4dh.com/nlp4dh-2024}{2024} \href{https://www.nlp4dh.com/nlp4dh-2025}{2025} \\
\noindent{Journal of Information Science} \\
\textit{Reviewer} \\
\noindent{PLOS ONE} \\
\textit{Reviewer} \\
\noindent{A-LIEP (Asian Library and Information Education and Practice)} 
\textit{Program Committee} \hfill \href{https://a-liep.org/}{2025} \\

\noindent \textbf{\underline{PERSONAL}} \\
\noindent Languages: Korean, English, Japanese, Python, R \\
\noindent Interests: Cooking, Running, Art, Architecture, Philosophy \\

\noindent \textbf{\underline{REFERENCES}} \\
\noindent Ryan Cordell, Associate Professor, School of Information Sciences, Department of English \\ 
University of Illinois at Urbana-Champaign \\
rcordell@illinois.edu \\

\noindent Ted Underwood, Professor, School of Information Sciences, Department of English \\
University of Illinois at Urbana-Champaign \\
tunder@illinois.edu \\

\noindent JooYoung Seo, Assistant Professor, School of Information Sciences \\
University of Illinois at Urbana-Champaign \\
jseo1005@illinois.edu \\

\noindent JungHwan Yang, Assistant Professor, Department of Communication \\
University of Illinois at Urbana-Champaign \\
junghwan@illinois.edu \\

\noindent David Smith, Associate Professor, Khoury College of Computer Sciences \\
Northeastern University \\
dasmith@northeastern.edu \\

\end{document}